High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
added lenet CNN

```{julia}
# Hyper:
_retrain = false
_regen = false

@@

@@

add_models = Dict(
    "Large MLP Ensemble" => mlp_large_ens,
)

@@

```{julia}
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = ["MLP", "MLP Ensemble", "Large Ensemble" "JEM", "JEM Ensemble"]
)
display(plt_additional_models)
savefig(plt, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

>>>>

```{julia}
# Hyper:
_retrain = false
_regen = true

@@

LeNet-5:

```{julia}
mutable struct LeNetBuilder
	filter_size::Int
	channels1::Int
	channels2::Int
end

function MLJFlux.build(b::LeNetBuilder, rng, n_in, n_out, n_channels)

	k, c1, c2 = b.filter_size, b.channels1, b.channels2

	mod(k, 2) == 1 || error("`filter_size` must be odd. ")

	# padding to preserve image size on convolution:
	p = div(k - 1, 2)

	front = Flux.Chain(
			   Conv((k, k), n_channels => c1, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Conv((k, k), c1 => c2, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Flux.flatten)
	d = Flux.outputsize(front, (n_in..., n_channels, 1)) |> first
    back = Flux.Chain(
        Dense(256, 120, relu),
        Dense(120, 84, relu),
        Dense(84, n_out),
    )
	return Flux.Chain(front, back)
end

# Final model:
lenet = ImageClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)

# Convert to image:
function toimg(X)
    X = matrix(X) |> x -> reshape(x, 28, 28, :)
    X = coerce(X, GrayImage)
    return X
end

lenet = (X -> toimg(X)) |> lenet
```

@@

add_models = Dict(
    "Large Ensemble" => mlp_large_ens,
    "LeNet-5" => lenet,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble", 
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
